Immutable Source-Mapped Abstract Syntax Tree:\ \\ A Design Pattern for Refactoring Engine APIs

### 2016-07-22 paper.tex
Added basic info on preprocessors, needs more work though.

@@

The situation gets a bit worse when changes are made to nested constructs.
Recall the example from Section~\ref{sec:Problem}, which reversed conditionals 
of \textit{if} statements. After the addition of the \textit{!} to the 
condition, the offset of the body is different. Consider a somewhat simplified 
example. Pictorially:

@@

\noindent
The body of the first \textit{if} statement begins at offset~6 in the original
code.  But after adding braces to the outer \textit{if} statement, the body of
the inner \textit{if} statement is shifted to offset~7. This must be taken into
account when the bodies of the \textit{if} and \textit{else} are switched.

>>>>

%TODO work on this preprocessor stuff some more
%Maybe move to a different place?
Preprocessors (such as the C preprocessor and M4), don't interfere with the ASTs
used by compilers. In most cases, the preprocessing is performed first, and the
output thereof is used to construct the AST. The lexer/parser requires no 
knowledge of the fact that the text was preprocessed.

Refactorings, however, are complicated by the C preprocessor. The grammar of 
preprocessor directives doesn't take into account C syntax, and can't be easily
represented in the C AST. This is the subject of Garrido's entire Ph.D.~thesis~%
\cite{garrido05program}. The compiler's method of preprocessing before parsing
can't be used, because the unpreprocessed text is what must be edited. The 
refactoring too must be able to parse, analyze, and transform code \textit{
with embedded preprocessor directives.}

The topic of refactoring preprocessed code will not be treated in detail here,
but suffice it to say that a compiler's AST will almost certainly be inadequate.
For more details, see Overbey et al.~\cite{wrt2009} and 
Garrido~\cite{garrido05program}.

@@

The situation gets a bit worse when changes are made to nested constructs.
Recall the example from Section~\ref{sec:Problem}, which reversed conditionals 
of \textit{if} statements. After the addition of the \textit{not} to the 
condition, the offset of the body is different. Consider a somewhat simplified 
example. Pictorially:

@@

\noindent
The body of the first \textit{if} statement begins at offset~6 in the original
code.  But after interchanging the body statements, the body of
the inner \textit{if} statement is shifted to offset~7. This must be taken into
account when the bodies of the \textit{if} and \textit{else} are switched.
